---
title: "SBP_Describe_Example2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SBP_Describe_Example2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sbp)
```

```{r}
#Example Data
library("penalized")
data(nki70)
library("riskRegression")
data(Melanoma)
```

The describe() method will provide descriptive information and statistics about the data provided.

In this example code, the describe() method will plot the Age data on a scatter plot, but also provide a text output detailing attributes of Age and a table of the descriptive statistics.

The visualization of Age is produced by default when running the describe() method.

```{r}
age=describe("Age",nki70)
```

Other parts of describe() can be accessed as attributes on the describe object.

$txt produces the text description of the data and features.

```{r}
age$txt
```

$tbl is an output of the descriptive statistics, including the five number summary, and a p-value for a test for normality.

```{r}
age$tbl
```

$method provides information on what testing procedures were used to obtain the descriptive information.

```{r}
age$method
```

$ref are the references associated with the use of the describe() method.

```{r}
age$ref
```
