---
title: "SBP_Model_Example1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SBP_Model_Example1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sbp)

#Example Data
library("penalized")
data(nki70)
library("riskRegression")
data(Melanoma)
```

model() produces a model of the data along with text output describing the metrics of the model.

```{r}
DIAPH3.FGF18=model(DIAPH3~FGF18,nki70)
```

$tbl displays the summary of the model coefficients, the upper and lower bounds for a 95% confidence interval around the coefficients, and the associated p-value.

```{r}
DIAPH3.FGF18$tbl
```

$txt is the description of all the information generated by model().

```{r}
DIAPH3.FGF18$txt
```

$method details the methods used to creating the model.

```{r}
DIAPH3.FGF18$method
```

$ref outputs the references used in the model() method.

```{r}
DIAPH3.FGF18$ref
```

Other display types of the information can be accessed by the 'fig', in this example fig is set to type 4, which produces a bar plot of correlation values.

```{r}
DIAPH3.FGF18=model(DIAPH3~FGF18,nki70,fig=4)
```

The model() method can also work with multiple linear regression and features the same attributes.

```{r}
FGF18.result=model(FGF18~Age+GSTM3,nki70)
```
